---
title: "Health Insurance Cross Sell - Part 02"
author: "Edneide Ramalho"
date: "`r format(Sys.time(), '%d/%m/%Y')`"
output: 
    html_document:
      highlight: textmate
      logo: logo.png
      theme: jou
      number_sections: yes
      toc: yes
      toc_float:
        collapsed: yes
        smooth_scroll: no
      df_print: paged
      code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Imports

```{r pacotes}
library(tidyverse)
library(janitor)
library(readr)
library(gtsummary)
library(summarytools)
library(kableExtra)
library(knitr)
library(gridExtra)
library(summarytools)
library(randomForest)
library(reshape2)
library(tidymodels)
```

# Helper Functions

## Top @K precision and recall

This function returns a dataframe with K rows. The last row will have the values of @K metrics.

```{r}
# Creating function  --------------------------
metrics_at_k_function <- function(model_name, model_results, k){
  
  df_results <- model_results %>% 
    arrange(desc(.pred_yes)) %>% 
    mutate(
      TP = ifelse(.pred_class == "yes" & response == "yes", 1, 0),
      FP = ifelse(.pred_class == "yes" & response == "no", 1, 0),
      FN = ifelse(.pred_class == "no" & response == "yes", 1, 0),
      TN = ifelse(.pred_class == "no" & response == "no", 1, 0)
      ) 
  
  # Create list for precision and recall
  precision_at_k <- list()
  recall_at_k <- list()

  # Populate the metric list
  for (i in 1:k) {
    subset_k <- df_results %>% 
    dplyr_row_slice(1:i)
    
    precision_at_k[[i]] <- (subset_k$TP %>% sum())/(subset_k$TP %>% sum() + subset_k$FP %>% sum())
  
    recall_at_k[[i]] <- (subset_k$TP %>% sum())/(subset_k$TP %>% sum() + subset_k$FN %>% sum())
}

  # Complete dataframe
    metrics_at_k_df <- df_results %>% 
      dplyr_row_slice(1:k) %>% 
      mutate(
        precision_at_k = unlist(precision_at_k),
        recall_at_k = unlist(recall_at_k)
        )
    
    final_at_k_df <- tibble(model = model_name, k = k) %>% 
      bind_cols(
        metrics_at_k_df %>% 
          slice(k) %>% 
          select(precision_at_k, recall_at_k)
      )
      
      
    
    return(list(metrics_at_k_df, final_at_k_df))
}
```

## Gain & Lift Curves

```{r}
curves_function <-  function(model_results){
  gain_plt <- gain_curve(model_results, response, .pred_yes) %>% 
  autoplot()
  
  lift_plt <- lift_curve(model_results, response, .pred_yes) %>%    autoplot()

  gridExtra::grid.arrange(gain_plt, lift_plt, ncol = 2)
}
```

# Data Collection

```{r}
df_selected <- readRDS("df_selected.rds")
```

# Pre-processing

```{r}
region_encoder <- readRDS("region_encoder.rds")
policy_encoder <- readRDS("policy_encoder.rds")

# Create function
encoder_function <- function(df){
  df %>% 
  left_join(region_encoder) %>% 
  select(-region_code) %>% 
  rename(region_code = region_num) %>% 
  left_join(policy_encoder) %>% 
  select(-policy_sales_channel) %>% 
  rename(policy_sales_channel = policy_num) 
}
```

```{r}
df_selected <- encoder_function(df_selected)
```

## Split into train and test datasets

```{r}
set.seed(123)

df_split <- df_selected %>% 
  initial_split(prop = 0.80, strata = response)

df_train <- df_split %>% 
  training()

df_test <- df_split %>% 
  testing()

```

## Applying steps

```{r}
# Write the recipe ------------------------
df_recipe <- recipe(response ~ .,
       data = df_train %>% select(-id)) %>% 
  step_normalize(age, days_associated) %>% 
  step_scale(health_annual_paid) %>% 
  step_dummy(all_nominal(), -all_outcomes())

# Train the recipe -----------------------
df_prep <- df_recipe %>% 
  prep(training = df_train)

df_train_preprocessed <- df_prep %>% 
  bake(new_data = df_train)

df_test_preprocessed <- df_prep %>% 
  bake(new_data = df_test)
```

# Logistic Regression 💻 

**Training time**: 2.27 seconds.

```{r, eval=FALSE}
# Model Specification -----------
logistic_model <- logistic_reg() %>% 
  set_engine('glm') %>% 
  set_mode('classification')

# Model Fitting -----------
start_time <- Sys.time()

logistic_fit <- logistic_model %>% 
  fit(response ~., 
      data = df_train_preprocessed)

end_time <- Sys.time()

print(end_time - start_time)

# Save result in RDS -----------
saveRDS(logistic_fit, "logistic_fit.rds")
```

```{r}
# Read RDS result -----------
logistic_fit <- readRDS("logistic_fit.rds")

# Prediction ----------
## Classes ------------
class_preds <- logistic_fit %>% 
  predict(new_data = df_test_preprocessed,
          type = 'class')
## Probabilities ------------
prob_preds <- logistic_fit %>% 
  predict(new_data = df_test_preprocessed,
          type = 'prob')

# Combine results -----------
lr_results <- df_test %>% 
  select(id, response) %>% 
  bind_cols(class_preds, prob_preds)

# Confusion Matrix ------------
confusion_matrix_lr <-  conf_mat(
  lr_results, truth = response, estimate = .pred_class
)

# Final @K Metrics --------------------
lr_metrics_at_K <- metrics_at_k_function(
  "Logistic Regression", 
  lr_results, 2000)
lr_metrics_at_K[[2]]

# Save metrics in RDS
saveRDS(lr_metrics_at_K, "lr_metrics_at_K.rds")

# Gain and lift curves ---------------
curves_function(lr_results)
```

**Gain**: By approaching 25% of the ordered list, \~60% of all interested customers are reached.

**Lift**: By approaching 25% of the ordered list, the model performs \~2.3 times better than the random list.

# Decision Tree 💻 

**Training time**: 0.97 segundos.

```{r, eval=FALSE}
# Model Specification -----------
dt_model <- decision_tree(tree_depth = 20) %>%
  set_engine("rpart") %>%
  set_mode("classification")

# Model Fitting -----------
start_time <- Sys.time()

dt_fit <- dt_model %>%
  fit(response ~ .,
      data = df_train_preprocessed)

end_time <- Sys.time()

print(end_time - start_time)

# Save result in RDS -----------
saveRDS(dt_fit, "dt_fit.rds")
```

```{r}
# Read RDS result -----------
dt_fit <- readRDS("dt_fit.rds")

# Prediction ----------
## Classes ------------
class_preds <- dt_fit %>% 
  predict(new_data = df_test_preprocessed,
          type = 'class')
## Probabilities ------------
prob_preds <- dt_fit %>% 
  predict(new_data = df_test_preprocessed,
          type = 'prob')

# Combine results -----------
dt_results <- df_test %>% 
  select(id, response) %>% 
  bind_cols(class_preds, prob_preds)

# Confusion Matrix ------------
confusion_matrix_dt <-  conf_mat(
  dt_results, truth = response, estimate = .pred_class
)

# Final @K Metrics --------------------
dt_metrics_at_K <- metrics_at_k_function(
  "Decision Tree", 
  dt_results, 2000)
dt_metrics_at_K[[2]]

# Save results in rds
saveRDS(dt_metrics_at_K, "dt_metrics_at_K")

# Gain and lift curves ---------------
# curves_function(dt_results)
```

For this model, in particular, it is not possible to plot the gain and lift curves, because there is no variation in the probabilities for "yes" and "no", as you can see below:

```{r}
dt_metrics_at_K[[1]] %>% 
  select(.pred_yes, .pred_no) %>% 
  summary()
```

# Decision Tree 💻 
