---
title: "Health Insurance Cross Sell - Part 03"
author: "Edneide Ramalho"
date: "`r format(Sys.time(), '%d/%m/%Y')`"
output: 
    html_document:
      highlight: textmate
      logo: logo.png
      theme: jou
      number_sections: yes
      toc: yes
      toc_float:
        collapsed: yes
        smooth_scroll: no
      df_print: paged
      code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Imports

```{r pacotes}
library(tidyverse)
library(janitor)
library(readr)
library(gtsummary)
library(summarytools)
library(kableExtra)
library(knitr)
library(gridExtra)
library(summarytools)
library(randomForest)
library(reshape2)
library(tidymodels)
```

# Helper Functions

## Encoder function

```{r}
region_encoder <- readRDS("region_encoder.rds")
policy_encoder <- readRDS("policy_encoder.rds")

encoder_function <- function(df){
  df %>% 
  left_join(region_encoder) %>% 
  select(-region_code) %>% 
  rename(region_code = region_num) %>% 
  left_join(policy_encoder) %>% 
  select(-policy_sales_channel) %>% 
  rename(policy_sales_channel = policy_num) 
}
```

## Top @K precision and recall

This function returns a dataframe with K rows. The last row will have the values of @K metrics.

```{r}
# Creating function  --------------------------
metrics_at_k_function <- function(model_name, model_results, k){
  
  df_results <- model_results %>% 
    arrange(desc(.pred_yes)) %>% 
    mutate(
      TP = ifelse(.pred_class == "yes" & response == "yes", 1, 0),
      FP = ifelse(.pred_class == "yes" & response == "no", 1, 0),
      FN = ifelse(.pred_class == "no" & response == "yes", 1, 0),
      TN = ifelse(.pred_class == "no" & response == "no", 1, 0)
      ) 
  
  # Create list for precision and recall
  precision_at_k <- list()
  recall_at_k <- list()

  # Populate the metric list
  for (i in 1:k) {
    subset_k <- df_results %>% 
    dplyr_row_slice(1:i)
    
    precision_at_k[[i]] <- (subset_k$TP %>% sum())/(subset_k$TP %>% sum() + subset_k$FP %>% sum())
  
    recall_at_k[[i]] <- (subset_k$TP %>% sum())/(subset_k$TP %>% sum() + subset_k$FN %>% sum())
}

  # Complete dataframe
    metrics_at_k_df <- df_results %>% 
      dplyr_row_slice(1:k) %>% 
      mutate(
        precision_at_k = unlist(precision_at_k),
        recall_at_k = unlist(recall_at_k)
        )
    
    final_at_k_df <- tibble(model = model_name, k = k) %>% 
      bind_cols(
        metrics_at_k_df %>% 
          slice(k) %>% 
          select(precision_at_k, recall_at_k)
      )
      
      
    
    return(list(metrics_at_k_df, final_at_k_df))
}
```

## Gain & Lift Curves

This function plot the gain and lift curves for the model.

```{r}
curves_function <-  function(model_results){
  gain_plt <- gain_curve(model_results, response, .pred_yes) %>% 
  autoplot()
  
  lift_plt <- lift_curve(model_results, response, .pred_yes) %>%    autoplot()
  
  return(gridExtra::grid.arrange(gain_plt, lift_plt, ncol = 2))
}
```

# Data Collection

```{r}
df_selected <- readRDS("df_selected.rds")
df_preprocessed <- encoder_function(df_selected)
```

# Spliting into train and test sets

```{r}
set.seed(123)

df_split <- df_preprocessed %>% 
  initial_split(strata = response)

df_train <- df_split %>% 
  training()

df_test <- df_split %>% 
  testing()
```

# Preprocessing

```{r}
# Featue engineering recipe
df_recipe <- recipe(response ~., data = df_train) %>%
  step_normalize(age, days_associated) %>%
  step_scale(health_annual_paid) %>% 
  step_dummy(all_nominal(), -all_outcomes())
```

# KFold cross validation

```{r}
df_kfolds <- vfold_cv(df_train, v = 5, strata = response)
```

# Models definition and hyperparameter tunning

## Logistic Regression 💻

Time to tune: 1.217322 mins

```{r}
# Model Specification ----------
lr_model <- logistic_reg(penalty = tune(), 
                         mixture = tune()) %>% 
  set_engine("glmnet") %>% 
  set_mode("classification")
```

```{r}
# See parameters
hardhat::extract_parameter_set_dials(lr_model)

# Using dials package
lr_grid <- grid_regular(extract_parameter_set_dials(lr_model), levels = 5)
```

```{r, eval=FALSE}
library(glmnet)

# Parallelize tuning process
doParallel::registerDoParallel()

# Tune package
start_time <- Sys.time()

lr_tune <- tune_grid(lr_model, df_recipe, 
                     resamples = df_kfolds,
                     grid = lr_grid)

end_time <- Sys.time()
print(end_time - start_time)

saveRDS(lr_tune, "lr_tune.rds")
```

```{r}
# Select the best hyperparameters -----------
lr_tune <- readRDS("lr_tune.rds")

lr_param <- lr_tune %>% 
  select_best("roc_auc")

# Apply the hyperparameters to the model ----------
tidy_lr_model <- finalize_model(lr_model, lr_param)

# Create workflow ----------
lr_wkfl <- workflow() %>% 
  add_model(tidy_lr_model) %>% 
  add_recipe(df_recipe)
```

```{r}
# Train the final model ----------------
doParallel::registerDoParallel()

start_time <- Sys.time()

# Train the model
lr_res <- last_fit(lr_wkfl, df_split)

end_time <- Sys.time()
print(round(end_time - start_time, 2))

time_training_lr <- end_time - start_time
saveRDS(time_training_lr, "time_training_lr.rds")

```

```{r}
# Confusion matrix
lr_res %>% 
  unnest(.predictions) %>% 
  conf_mat(truth = response, estimate = .pred_class)
```

As we can see, the model classified all the client intention to sign for a new insurance as "no", even with the parameter tunning.

```{r}
lr_results <- lr_res %>% 
  unnest(.predictions) %>% 
  select(.pred_yes:response)

lr_metrics_at_k <- metrics_at_k_function("Logistic Regression", lr_results, 2000)

lr_metrics_at_k[[2]]
```
